\section{Conclusion and Future Work}

\subsection{Conclusion}
We demonstrated that our linear model provided us with more equal results for both the distance model and 
the acceleration model.
This highlights the effectiveness of using a linear model as a discrete integration system.
A comparison with the previously used ballistic integration method revealed significantly better performance in terms of accuracy.
Finally, using the coefficients obtained from linear regression, 
we were able to predict both distance and velocity with high accuracy
Although some small error was observed, these results might be sufficient for our neural network.
Visualizations of these predictions showcased their alignment with the ground truth, further validating the effectiveness of our integration model.

Integral to enhancing our model's precision, the filtering module plays an essential role in preprocessing and refining the data for improved analysis. By systematically identifying key vehicle behaviors through advanced algorithms, this module enables a more nuanced understanding of driving dynamics. This layered approach, combining both granular observation and broader behavioral patterns, enriches our dataset, allowing for a more robust and accurate prediction model. By integrating this layered understanding of social dynamics, the filtering module not only identifies basic maneuvers but also interprets these actions within the broader context of social interaction, thereby enriching the predictive model with a more refined representation of real-world driving conditions. This enhancement significantly increases the model’s ability to accurately predict vehicle behaviors, marking an improvement over traditional predictive models by incorporating a deeper comprehension of the complex interplay between individual actions and social influences in driving scenarios

\subsection{Future Work}
In future work, we plan to continue refining our integration model to achieve even better results by further fine-tuning its parameters and training procedures. 

Additionally, we aim to explore the integration of our discrete integration model with the neural network developed by the previous team.
By testing the combined model and comparing its effectiveness against the old method, we can gain insights into its actual performance. 

Furthermore, we plan to extend the scope of vehicle behaviours our filtering module can detect, incorporating a wider range of complex driving actions and social interactions. This will involve not only enhancing the algorithmic composure of the module but also diversifying and expanding our datasets to cover more varied and challenging driving scenarios. By doing so, we aim to achieve a richer, more detailed understanding of driver behaviour, further improving the predictive accuracy and reliability of our autonomous driving systems.